The Marshall and Olkin-G and Gamma-G family of distributions: properties and applications

### 2022-06-17 paper/paper.tex
Ultimas modificações no paper

\newcommand{\etn}{{\mbox{\boldmath $\eta$}}} 
\hyphenation{ge-ne-ra-ted  hy-per-geo-me-tric  cha-rac-te-ri-ze}

@@

\vspace{1.5cm}
\title{\color{red}{The Marshall and Olkin-G and Gamma-G family of distributions: properties and applications
	%\footnote{The opinions expressed in this text are those of the authors and do not necessarily reflect the views of any organization.}
}}
\renewcommand{\titleheading}
{The MOGG family of distributions}  % --- on odd running heads

\author{\authoraddress{Maria do Carmo S. Lima \href{https://orcid.org/0000-0002-5480-3103}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}} 
	{Department of Statistics,
		Federal University of Pernambuco,\\
        Pernambuco, Recife, Brazil
		\ (maria@de.ufpe.br)}
	\\
	\authoraddress{Gauss M. Cordeiro \href{https://orcid.org/0000-0002-3052-6551}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}}
	{Department of Statistics,
		Federal University of Pernambuco,\\
		Pernambuco, Recife, Brazil
		\ (gauss@de.ufpe.br)}
	\\
	\authoraddress{Pedro Rafael D. Marinho \href{https://orcid.org/0000-0003-1591-8300}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}
	\correspondingauthor}
	{Department of Statistics,
		Federal University of Paraíba,\\
		Paraíba, João Pessoa, Brazil
		\ (pedro.rafael.marinho@gmail.com)}
}
\renewcommand{\authorheading}
{Maria do Carmo S. Lima, Gauss M. Cordeiro and Pedro Rafael D. Marinho, }  % --- on even running heads

@@

%-------------------------------------------------------------------------------
% Just asking LaTeX to effectively do the title...
%-------------------------------------------------------------------------------
\maketitle
%-------------------------------------------------------------------------------
% Just asking LaTeX to numerate lines...
%-------------------------------------------------------------------------------
\setpagewiselinenumbers
\modulolinenumbers[1]
\linenumbers
%%%%%%%%%%%%%%%%%%%%%%%%%% alteracao: Datas %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
~~~~{\small{\sffamily Received:} December 2020 ~~~~~~{\sffamily Revised:} May 2022 ~~~~~~{\sffamily Accepted:} Month 0000}
%%%%%%%%%%%%%%%%%%%%%%%%%% alteracao %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\textcolor{red}{The advances in the field of Data Science requires the search for new fa\-milies of distributions that adequately model real data has been increasing steadily in the last years.  The construction of different generation methods and even generators of families has made it difficult to compare new proposals. In the midst of a huge set of existing families in the literature of new distributions, to find a proposal that is in fact an excellent competitor when compared to other existing ones, in terms of adjustment to real data sets and also that does not present estimation problems, is a major challenge.}

\textcolor{red}{The classes of distributions in the early 1980s were based on the simple idea of adding parameters to a baseline distribution.} The mechanism by adding shape parameters to a baseline distribution has proved to be useful to make the 
generated distributions more flexible especially for studying 
tail properties than existing ones and for improving their goodness-of-fit statistics to real data. Many special 
distributions in these families are discussed by Tahir and Nadarajah (2015).

\textcolor{red}{The addition of parameters in the construction of new distributions/families was improved by the inclusion of mathematical functions known in the literature, such as beta and gamma functions, for example, which produce new generators 
with more flexible properties than their baselines. 
Two well-known examples are the beta-G (Eugene et al., 2002) 
and gamma-G (Zografos and Balakrishnan, 2009) generators.}

\textcolor{red}{However, the inclusion of such functions for generating new families brought, in some cases, problems for parameter estimation. So, despite the fit being more suitable for some types of data and, therefore, having a superior performance when compared to other generators, the estimation process can 
often be a problem.}

\textcolor{red}{In this context, this work presents a new family obtained by composing a very competitive class in the literature with another class that has the gamma function in its structure.}

Let $G(x)$ be the cumulative distribution function (CDF) of a
baseline distribution and $g(x)=dG(x)/dx$ be the corresponding  probability density function (PDF) depending on a
parameter vector $\eta$. A generalized family is presented
with two extra shape parameters by transforming the CDF $G(x)$
according to two sequential important classes. 
These classes, \textcolor{red}{called Marshall and Olkin-G
and Gamma-G}, are important for modeling data in several areas,  \textcolor{red}{and they are reviewed below}.

The CDF of the Marshall and Olkin's (1997) ($\text{MO-G}$) 
class (for $\theta>0$) is
\begin{equation}\label{CDF_MO}
F_{\text{MO-G}}(x)=\frac{G(x)}{\theta+(1-\theta)G(x)}=\frac{G(x)}{1-(1-\theta)[1-G(x)]},\quad x \in \mathbb{R}.
\end{equation}

@@

Tahir and Nadarajah (2015, Table 2) presented thirty 
distributions belonging to this family. It is easily generated 
from the baseline quantile function (QF) by
$Q_{\text{MO-G}}(u)=Q_{G}\left(\theta u / \left[\theta u+1-u\right]\right)$ for $u\in(0,1)$.

@@

The CDF of the gamma-G ($\Gamma$-G) class (Zografos and Balakrishnan, 2009) is
\begin{eqnarray}\label{CDF_Ga}
F_{\Gamma\text{-G}}(x)=\gamma_1\left( a, -\log \left[1-G(x)\right]\right), \quad x \in \mathbb{R},
\end{eqnarray}
where $a>0$ is an extra shape parameter, $\gamma_1(a,z)= \gamma(a,z)/\Gamma(a)$ is the incomplete gamma function ratio, 
and $\gamma(a,z)=\int_0^{z} t^{a-1}\,\rm{e}^{-t}dt$.

@@

The MOGa-G family can be fitted to real data using the {\bf AdequacyModel} package ({\color{red}Marinho et al., 2019}) 
in the {\sf R} software. This packa\-ge does not require to 
define the log-likelihood function, and it computes the MLEs, 
their standard errors (SEs), and the formal statistics defined 
in Section \ref{applications}. It is only necessary to provide the
PDF and CDF of the distribution to be fitted to a data set.

For example, if $x_i$ is one observation from (\ref{PDF_MO-Gamma-G}) and $\etn$ is a $q$-parameter vector specifying $G(\cdot)$ \textcolor{red}{as the Weibull CDF}, the log-likelihood function for $\boldsymbol{\theta}^\top=(a,\theta,\etn^\top)$ from $n$ observations can be expressed as 
\begin{align}\label{loglik}
\ell (\boldsymbol{\theta})=&\,n\log (\theta)+n\log(\gamma)+n\, a\, \gamma \log(\lambda)+(a\gamma-1)\sum_{i=1}^n{\log(x_i)}-\lambda^\gamma\sum_{i=1}^n{\log(x_i)}\nonumber \\ &
-n\log[\Gamma(a)]-2\sum_{i=1}^n{\log\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x_i)^\gamma]\}}.
\end{align}

@@

The {\bf AdequacyModel} package of the programming language {\sf R} is used to obtain the MLEs, see R Core Team (2020). This library, created and maintained by one of the authors of this paper,
is widely cited by several works in statistics, and serves as 
a basis for other library implementations available on the Comprehensive R Archive Network (CRAN). By using the goodness.fit function, it is possible to provide an implementation  
of (\ref {PDF_MO-Gamma-G}), and obtain $\ell(\cdot)$ by returning the MLEs, and some measures of adequacy of fit. Further details regarding this package can be obtained from Marinho et al. (2019).

@@

{\color{red}Due to the probable absence of MLEs in closed-form for distributions belonging to the MOGa-G family, it is necessary to examine the precision of the estimates calculated numerically.

@@

The simulations are performed on a computer with an Intel(R) Core(TM) i5-9500 CPU processor with 6 threads working at a maximum frequency of 3.00GHz, requiring, on this hardware, a time of 15.4828 hours to perform all simulations, 7.7414 hours for the MOGa-Dagum($\theta, a, \alpha, \beta, p$) distribution, 
and 4.9688 hours for the MOGa-Weibull($\theta, a, \lambda, \gamma$) distribution. Tables \ref{tab:bias1} and  \ref{tab:bias2} 
reveal that the average biases of the MLEs could be very small for $n>2,000$.}

@@

The constant $c$ must be chosen in such a way that $\frac{f(y)}{c \,g (y)}\leq 1 $. Thus, to minimize the computational cost of generating observations from $X$ through the generated observations from $Y$, $c$ is chosen as the lowest possible value to maximize the likelihood of acceptance. Further details of this method can be found in Rizzo (2019).

\begin{table}[H]
\centering
\caption{\textcolor{red}{Average biases of the MLEs of the MOGa-Dagum($\theta, a, \alpha, \beta, p$) distri\-bu\-tion 
calculated by the BFGS method from simulations.}}\label{tab:bias1}
	\begin{tabular}{rrrrrrr}
		\hline
		$n$ & $B(\hat{\theta})$ & $B(\hat{a})$ & $B(\hat{\alpha})$ & $B(\hat{\beta})$ & $B(\hat{p})$ & Time (mins)\\
		\hline
10 & 0.2213 & 2.1944 & 2.6971 & 1.5803 & 1.3190 & 0.6960 \\ 
20 & 0.4240 & 2.4793 & 1.5591 & 1.8083 & 0.7414 & 0.9819 \\ 
60 & 0.7458 & 2.2661 & 0.5598 & 1.8495 & 0.2812 & 1.9417 \\ 
100 & 0.6194 & 1.9438 & 0.3312 & 1.6142 & 0.2935 & 2.7208 \\ 
200 & 0.3950 & 1.4262 & 0.1856 & 1.1556 & 0.3611 & 4.4534 \\ 
400 & 0.2077 & 0.9599 & 0.1082 & 0.6157 & 0.4076 & 7.4698 \\ 
600 & 0.1200 & 0.7213 & 0.0767 & 0.4024 & 0.3572 & 9.4975 \\ 
1000 & 0.0629 & 0.4791 & 0.0503 & 0.2123 & 0.2584 & 12.4221 \\ 
2000 & 0.0362 & 0.2958 & 0.0298 & 0.1145 & 0.1878 & 20.7251 \\ 
5000 & -0.0040 & 0.1325 & 0.0159 & 0.0144 & 0.0167 & 28.3380 \\ 
10000 & -0.0133 & 0.0815 & 0.0096 & 0.0081 & 0.0039 & 50.9298 \\ 
20000 & -0.0111 & 0.0349 & 0.0037 & 0.0006 & -0.0109 & 68.6320 \\ 
30000 & -0.0036 & 0.0191 & 0.0006 & -0.0041 & -0.0034 & 97.3046 \\ 
50000 & -0.0057 & 0.0129 & 0.0016 & 0.0015 & -0.0026 & 158.3737 \\ 
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
\caption{\textcolor{red}{Average biases of the MLEs of the MOGa-Weibull($\theta, a, \lambda, \gamma$) distribution calculated 
by the BFGS method from simulations.}}\label{tab:bias2}
	\begin{tabular}{rrrrrr}
		\hline
		$n$ & $B(\hat{\theta})$ & $B(\hat{a})$ & $B(\hat{\lambda})$ & $B(\hat{\gamma})$ & Time (mins)\\
		\hline
		10 & 0.0818 & 0.1362 & 4.9274 & 1.2407 & 0.6716 \\ 
		20 & 0.3404 & -0.0177 & 3.4160 & 1.4117 & 0.8077 \\ 
		60 & 0.7037 & -0.0677 & 1.8806 & 1.3385 & 1.1773 \\ 
		100 & 0.6698 & -0.0535 & 1.3684 & 1.1796 & 1.2643 \\ 
		200 & 0.5371 & -0.0299 & 0.8265 & 0.9110 & 1.7886 \\ 
		400 & 0.3371 & -0.0047 & 0.4205 & 0.5967 & 2.8386 \\ 
		600 & 0.2457 & 0.0076 & 0.2685 & 0.4306 & 3.6867 \\ 
		1000 & 0.1476 & 0.0093 & 0.1553 & 0.2818 & 5.0944 \\ 
		2000 & 0.0731 & 0.0035 & 0.0758 & 0.1530 & 8.8577 \\ 
		5000 & 0.0264 & 0.0007 & 0.0283 & 0.0618 & 15.8586 \\ 
		10000 & 0.0128 & -0.0007 & 0.0142 & 0.0318 & 29.8629 \\ 
		20000 & 0.0053 & -0.0012 & 0.0071 & 0.0160 & 48.7417 \\ 
		30000 & 0.0023 & -0.0014 & 0.0053 & 0.0119 & 64.7387 \\ 
		50000 & 0.0023 & -0.0004 & 0.0028 & 0.0063 & 112.7422 \\ 
		\hline
\end{tabular}
\end{table}

@@

Two applications compare the MOGa-Weibull (MOGa-W for short) 
model with seven extended Weibull distributions: the 
beta-Weibull ($\beta$-W) (Famoye et al., 2005), 
Kumaraswamy Weibull (Kw-W) (Cordeiro et al., 2010), 
Marshall-Olkin Weibull (MO-W) (Ahmed et al., 2017), 
Marshall-Olkin Extended Weibull (MOE-W) (Cordeiro et al., 2019), exponentiated Weibull (exp-W) (Mudholkar and Srivastava, 1993), gamma Weibull ($\Gamma$-W) (Cordeiro et al., 2016), 
and exponentiated generalized Weibull 
(EG-W) (Oguntunde et al., 2015) (with $a=1$). Some of 
these distributions are widely used in practice.

@@

The {\bf AdequacyModel} package is used to fit the 
previous distributions to two real data sets. The SANN method, which is a variant of simulated annealing algorithm (Belisle, 1992), is used here. The distributions are compared 
via the Anderson Darling (A$^{*}$) and Cram\'er Von Mises (W$^{*}$) statistics reported in the {\tt goodness.fit} function.

For the first case, the {\bf betareg} package is applied to a modification of the ``FoodExpenditure'' data, which refer to 
the proportions of income spent on food for 38 households 
in a large US city (according to the package information). The household expenditures for food are given by
\begin{eqnarray*}
data = FoodExpenditure_{food} / \#(FoodExpenditure_{food}),
\end{eqnarray*}
where $FoodExpenditure_{food}$ is the random variable 
corresponding to the household expenditures for food, and $\#(\cdot)$ indicates the number of observations on this variable. \textcolor{red}{The observations for the first data set are given bellow:\\
  0.4210000, 0.4382105, 0.5721316, 0.1955526, 0.2758158, 0.3565263,
  0.6120000, 0.4730526, 0.3726579, 0.2322368, 0.3732632, 0.5158947,
  0.3612632, 0.5563421, 0.4591053, 0.2533947, 0.3685526, 0.2410526,
  0.4955526, 0.2010789, 0.3653158, 0.2544737, 0.5685263, 0.2859474,
  0.7626316, 0.2863684, 0.4884474, 0.3060263, 0.4754474, 0.3826053,
  0.5050526, 0.6820526, 0.7587632, 0.4176053, 0.3923684, 0.2513158,
  0.6070000, 0.3881842.}

\textcolor{red}{Some descriptive statistics are reported in Table \ref{tabds}. The minimum value refers to a family of 3 people and income of 39,151, which does not represent the lowest family 
income for the current data, as expected, occupying only the 
fifth position among those with the lowest income. The maximum value corresponds to a family of 6 people with an income of 69,929, the second-largest number among the number of people per family in the group in question. Furthermore, we can note that the current data  present positive asymmetry and negative kurtosis.}

\textcolor{red}{In addition, the standard deviation is relatively low. Figure \ref{ttt} displays the total time on test (TTT) plot for the first data set, which shows that the failure function is decreasing. So, the MOGa-W distribution is appropriate to fit 
these data, since its  hazard function presents this shape (see,  Figure \ref{fig:hazard}).}

@@

A data set collected in a pilot study about hypertension in the Dominican Republic in 1997 refers to the second application. The observations are the systolic blood pressure of persons who 
came to medical clinics in several villages for a variety of complaints. 
\textcolor{red}{The observations for the data set in question are:} 

@@

\textcolor{red}{Table \ref{tabds2} provides the descriptive statistics for the second data set. Consi\-dering that the systolic blood pressure represents the highest number presented in the pressure measuring equipment, the maximum (236) found in this 
table should represent an individual with serious heart problems. This is due to the fact that the normal systolic pressure is 120.}

 \textcolor{red}{The minimum value (80) should be for 
 an individual who probably suffers from low blood pressure. Also note that the data set has positive skewness. This indicates that few people have high pressure values and, in this case, the mode is 120, which represents a good value for systolic pressure.}

 \textcolor{red}{Figure \ref{ttt2} provides the TTT plot 
 for the second clinic data, which shows that the hazard function is decreasing, thus supporting the MOGa-W model.}

@@

\item
M.H. Tahir, S. Nadarajah:
Parameter induction in continuous univariate distributions: Well-established G families.
Anais da Academia Brasileira de Ci\^{e}ncias {\bf 87} 539-568 (2015).

\item
A.W. Marshall, I. Olkin:
A new method for adding a parameter to a family of distributions with
application to the exponential and Weibull families.
Biometrika {\bf 84} 641-652 (1997).

\item
K. Zografos, N. Balakrishnan:
On families of beta-and generalized gamma-generated distribution and
associate inference.  Statistical Methodology {\bf 6} 344-362 (2009).

>>>>

\usepackage{hyperref}
\hypersetup{
	pdftoolbar=true,        % show Acrobat’s toolbar?
	pdfmenubar=true,        % show Acrobat’s menu?
	pdffitwindow=true,     % window fit to page when opened
	pdfstartview={FitH},    % fits the width of the page to the window
	pdftitle={title},    % title
	pdfauthor={Salvatore Mazzarino},     % author
	pdfsubject={Subject},   % subject of the document
	pdfcreator={Salvatore Mazzarino},   % creator of the document
	pdfproducer={Salvatore Mazzarino}, % producer of the document
	pdfkeywords={Green Networking} {Mobile Cloud} {Network Coding} {Energy}, % list of keywords
	pdfnewwindow=true,      % links in new window
	colorlinks=true,       % false: boxed links; true: colored links
	linkcolor=blue,          % color of internal links (change box color with linkbordercolor)
	citecolor=blue,        % color of links to bibliography
	filecolor=magenta,      % color of file links
	urlcolor=magenta           % color of external links
}
\newcommand{\etn}{{\mbox{\boldmath $\eta$}}} 
\hyphenation{ge-ne-ra-ted  hy-per-geo-me-tric  cha-rac-te-ri-ze}

@@

\vspace{1.5cm}
\title{The Marshall and Olkin-G and Gamma-G family of distributions: properties and applications}

\renewcommand{\titleheading}
{The MOGG family of distributions}  % --- on odd running heads

\author{\authoraddress{Maria do Carmo S. Lima \href{https://orcid.org/0000-0002-5480-3103}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}} 
	{Department of Statistics,
		Federal University of Pernambuco,\\
        Pernambuco, Recife, Brazil
        \href{maria@de.ufpe.br}{maria@de.ufpe.br}}
	\\
	\authoraddress{Gauss M. Cordeiro \href{https://orcid.org/0000-0002-3052-6551}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}}
	{Department of Statistics,
		Federal University of Pernambuco,\\
		Pernambuco, Recife, Brazil
		\href{gauss@de.ufpe.br}{gauss@de.ufpe.br}}
	\\
	\authoraddress{Pedro Rafael D. Marinho \href{https://orcid.org/0000-0003-1591-8300}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}
	\correspondingauthor}
	{Department of Statistics,
		Federal University of Paraíba,\\
		Paraíba, João Pessoa, Brazil
		\href{pedro.rafael.marinho@gmail.com}{pedro.rafael.marinho@gmail.com}}
}
\renewcommand{\authorheading}
{Maria do Carmo S. Lima, Gauss M. Cordeiro and Pedro Rafael D. Marinho, }  % --- on even running heads

@@

%-------------------------------------------------------------------------------
% Just asking LaTeX to effectively do the title...
%-------------------------------------------------------------------------------
\maketitle
%-------------------------------------------------------------------------------
% Just asking LaTeX to numerate lines...
%-------------------------------------------------------------------------------
\setpagewiselinenumbers
\modulolinenumbers[1]
%\linenumbers
%%%%%%%%%%%%%%%%%%%%%%%%%% alteracao: Datas %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
~~~~{\small{\sffamily Received:} December 2020 ~~~~~~{\sffamily Revised:} May 2022 ~~~~~~{\sffamily Accepted:} Month 0000}
%%%%%%%%%%%%%%%%%%%%%%%%%% alteracao %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The advances in the field of Data Science requires the search for new fa\-milies of distributions that adequately model real data has been increasing steadily in the last years.  The construction of different generation methods and even generators of families has made it difficult to compare new proposals. In the midst of a huge set of existing families in the literature of new distributions, to find a proposal that is in fact an excellent competitor when compared to other existing ones, in terms of adjustment to real data sets and also that does not present estimation problems, is a major challenge.

The classes of distributions in the early 1980s were based on the simple idea of adding parameters to a baseline distribution. The mechanism by adding shape parameters to a baseline distribution has proved to be useful to make the 
generated distributions more flexible especially for studying  tail properties than existing ones and for improving their goodness-of-fit statistics to real data. Many special  distributions in these families are discussed by Tahir and Nadarajah (2015) \cite{Tahir}.

The addition of parameters in the construction of new distributions/families was improved by the inclusion of mathematical functions known in the literature, such as beta and gamma functions, for example, which produce new generators with more flexible properties than their baselines. Two well-known examples are the beta-G (Eugene et al., 2002)  \cite{Eugene} and gamma-G (Zografos and Balakrishnan, 2009) \cite{Zografos} generators.

However, the inclusion of such functions for generating new families brought, in some cases, problems for parameter estimation. So, despite the fit being more suitable for some types of data and, therefore, having a superior performance when compared to other generators, the estimation process can  often be a problem.

In this context, this work presents a new family obtained by composing a very competitive class in the literature with another class that has the gamma function in its structure.

Let $G(x)$ be the cumulative distribution function (CDF) of a baseline distribution and $g(x)=dG(x)/dx$ be the corresponding  probability density function (PDF) depending on a parameter vector $\eta$. A generalized family is presented with two extra shape parameters by transforming the CDF $G(x)$ according to two sequential important classes.  These classes, called Marshall and Olkin-G and Gamma-G, are important for modeling data in several areas,  and they are reviewed below.

The CDF of the Marshall and Olkin's (1997) \cite{Marshall} ($\text{MO-G}$) 
class (for $\theta>0$) is
\begin{equation}\label{CDF_MO}
F_{\text{MO-G}}(x)=\frac{G(x)}{\theta+(1-\theta)G(x)}=\frac{G(x)}{1-(1-\theta)[1-G(x)]},\quad x \in \mathbb{R}.
\end{equation}

@@

Tahir and Nadarajah (2015, Table 2) \cite{Tahir} presented thirty  distributions belonging to this family. It is easily generated  from the baseline quantile function (QF) by $Q_{\text{MO-G}}(u)=Q_{G}\left(\theta u / \left[\theta u+1-u\right]\right)$ for $u\in(0,1)$.

@@

The CDF of the gamma-G ($\Gamma$-G) class (Zografos and Balakrishnan, 2009) \cite{Zografos}  is
\begin{eqnarray}\label{CDF_Ga}
F_{\Gamma\text{-G}}(x)=\gamma_1\left( a, -\log \left[1-G(x)\right]\right), \quad x \in \mathbb{R},
\end{eqnarray}
where $a>0$ is an extra shape parameter, $\gamma_1(a,z)= \gamma(a,z)/\Gamma(a)$ is the incomplete gamma function ratio, 
and $\gamma(a,z)=\int_0^{z} t^{a-1}\,\rm{e}^{-t}dt$.

@@

The MOGa-G family can be fitted to real data using the {\bf AdequacyModel} package (Marinho et al., 2019)  \cite{Marinho} in the {\sf R} software. This packa\-ge does not require to  define the log-likelihood function, and it computes the MLEs,  their standard errors (SEs), and the formal statistics defined  in Section \ref{applications}. It is only necessary to provide the PDF and CDF of the distribution to be fitted to a data set.

For example, if $x_i$ is one observation from (\ref{PDF_MO-Gamma-G}) and $\etn$ is a $q$-parameter vector specifying $G(\cdot)$ as the Weibull CDF, the log-likelihood function for $\boldsymbol{\theta}^\top=(a,\theta,\etn^\top)$ from $n$ observations can be expressed as 
\begin{align}\label{loglik}
\ell (\boldsymbol{\theta})=&\,n\log (\theta)+n\log(\gamma)+n\, a\, \gamma \log(\lambda)+(a\gamma-1)\sum_{i=1}^n{\log(x_i)}-\lambda^\gamma\sum_{i=1}^n x_i^\gamma\nonumber \\ &
-n\log[\Gamma(a)]-2\sum_{i=1}^n{\log\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x_i)^\gamma]\}}.
\end{align}

@@

The {\bf AdequacyModel} package of the programming language {\sf R} is used to obtain the MLEs, see R Core Team (2020) \cite{Team}. This library, created and maintained by one of the authors of this paper,
is widely cited by several works in statistics, and serves as 
a basis for other library implementations available on the Comprehensive R Archive Network (CRAN). By using the goodness.fit function, it is possible to provide an implementation  
of (\ref {PDF_MO-Gamma-G}), and obtain $\ell(\cdot)$ by returning the MLEs, and some measures of adequacy of fit. Further details regarding this package can be obtained from Marinho et al. (2019) \cite{Marinho}.

@@

Due to the probable absence of MLEs in closed-form for distributions belonging to the MOGa-G family, it is necessary to examine the precision of the estimates calculated numerically.

@@

The simulations are performed on a computer with an Intel(R) Core(TM) i5-9500 CPU processor with 6 threads working at a maximum frequency of 3.00GHz, requiring, on this hardware, a time of 15.4828 hours to perform all simulations, 7.7414 hours for the MOGa-Dagum($\theta, a, \alpha, \beta, p$) distribution, 
and 4.9688 hours for the MOGa-Weibull($\theta, a, \lambda, \gamma$) distribution. Tables \ref{tab:bias1} and  \ref{tab:bias2} 
reveal that the average biases of the MLEs could be very small for $n>2,000$.

@@

The constant $c$ must be chosen in such a way that $\frac{f(y)}{c \,g (y)}\leq 1 $. Thus, to minimize the computational cost of generating observations from $X$ through the generated observations from $Y$, $c$ is chosen as the lowest possible value to maximize the likelihood of acceptance. Further details of this method can be found in Rizzo (2019) \cite{Rizzo}.

\begin{table}[H]
\centering
\caption{Average biases of the MLEs of the MOGa-Dagum($\theta, a, \alpha, \beta, p$) distri\-bu\-tion 
calculated by the BFGS method from simulations.}\label{tab:bias1}
	\begin{tabular}{rrrrrrr}
		\hline
		$n$ & $B(\hat{\theta})$ & $B(\hat{a})$ & $B(\hat{\alpha})$ & $B(\hat{\beta})$ & $B(\hat{p})$ & Time (mins)\\
		\hline
10 & 0.2213 & 2.1944 & 2.6971 & 1.5803 & 1.3190 & 0.6960 \\ 
20 & 0.4240 & 2.4793 & 1.5591 & 1.8083 & 0.7414 & 0.9819 \\ 
60 & 0.7458 & 2.2661 & 0.5598 & 1.8495 & 0.2812 & 1.9417 \\ 
100 & 0.6194 & 1.9438 & 0.3312 & 1.6142 & 0.2935 & 2.7208 \\ 
200 & 0.3950 & 1.4262 & 0.1856 & 1.1556 & 0.3611 & 4.4534 \\ 
400 & 0.2077 & 0.9599 & 0.1082 & 0.6157 & 0.4076 & 7.4698 \\ 
600 & 0.1200 & 0.7213 & 0.0767 & 0.4024 & 0.3572 & 9.4975 \\ 
1000 & 0.0629 & 0.4791 & 0.0503 & 0.2123 & 0.2584 & 12.4221 \\ 
2000 & 0.0362 & 0.2958 & 0.0298 & 0.1145 & 0.1878 & 20.7251 \\ 
5000 & -0.0040 & 0.1325 & 0.0159 & 0.0144 & 0.0167 & 28.3380 \\ 
10000 & -0.0133 & 0.0815 & 0.0096 & 0.0081 & 0.0039 & 50.9298 \\ 
20000 & -0.0111 & 0.0349 & 0.0037 & 0.0006 & -0.0109 & 68.6320 \\ 
30000 & -0.0036 & 0.0191 & 0.0006 & -0.0041 & -0.0034 & 97.3046 \\ 
50000 & -0.0057 & 0.0129 & 0.0016 & 0.0015 & -0.0026 & 158.3737 \\ 
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
\caption{Average biases of the MLEs of the MOGa-Weibull($\theta, a, \lambda, \gamma$) distribution calculated 
by the BFGS method from simulations.}\label{tab:bias2}
	\begin{tabular}{rrrrrr}
		\hline
		$n$ & $B(\hat{\theta})$ & $B(\hat{a})$ & $B(\hat{\lambda})$ & $B(\hat{\gamma})$ & Time (mins)\\
		\hline
		10 & 0.0818 & 0.1362 & 4.9274 & 1.2407 & 0.6716 \\ 
		20 & 0.3404 & -0.0177 & 3.4160 & 1.4117 & 0.8077 \\ 
		60 & 0.7037 & -0.0677 & 1.8806 & 1.3385 & 1.1773 \\ 
		100 & 0.6698 & -0.0535 & 1.3684 & 1.1796 & 1.2643 \\ 
		200 & 0.5371 & -0.0299 & 0.8265 & 0.9110 & 1.7886 \\ 
		400 & 0.3371 & -0.0047 & 0.4205 & 0.5967 & 2.8386 \\ 
		600 & 0.2457 & 0.0076 & 0.2685 & 0.4306 & 3.6867 \\ 
		1000 & 0.1476 & 0.0093 & 0.1553 & 0.2818 & 5.0944 \\ 
		2000 & 0.0731 & 0.0035 & 0.0758 & 0.1530 & 8.8577 \\ 
		5000 & 0.0264 & 0.0007 & 0.0283 & 0.0618 & 15.8586 \\ 
		10000 & 0.0128 & -0.0007 & 0.0142 & 0.0318 & 29.8629 \\ 
		20000 & 0.0053 & -0.0012 & 0.0071 & 0.0160 & 48.7417 \\ 
		30000 & 0.0023 & -0.0014 & 0.0053 & 0.0119 & 64.7387 \\ 
		50000 & 0.0023 & -0.0004 & 0.0028 & 0.0063 & 112.7422 \\ 
		\hline
\end{tabular}
\end{table}

@@

Two applications compare the MOGa-Weibull (MOGa-W for short) 
model with seven extended Weibull distributions: the 
beta-Weibull ($\beta$-W) (Famoye et al., 2005) \cite{Famoye}, 
Kumaraswamy Weibull (Kw-W) (Cordeiro et al., 2010) \cite{Cordeiro_2010}, 
Marshall-Olkin Weibull (MO-W) (Ahmed et al., 2017) \cite{Ahmad}, 
Marshall-Olkin Extended Weibull (MOE-W) (Cordeiro et al., 2019) \cite{Cordeiro_2019}, exponentiated Weibull (exp-W) (Mudholkar and Srivastava, 1993) \cite{Mudholkar}, gamma Weibull ($\Gamma$-W) (Cordeiro et al., 2016) \cite{Cordeiro_2016}, 
and exponentiated generalized Weibull 
(EG-W) (Oguntunde et al., 2015) \cite{Oguntunde} (with $a=1$). Some of 
these distributions are widely used in practice.

@@

The {\bf AdequacyModel} package is used to fit the 
previous distributions to two real data sets. The SANN method, which is a variant of simulated annealing algorithm (Belisle, 1992) \cite{Belisle}, is used here. The distributions are compared 
via the Anderson Darling (A$^{*}$) and Cram\'er von Mises (W$^{*}$) statistics reported in the {\tt goodness.fit} function.

For the first case, the {\bf betareg} package is applied to a modification of the ``FoodExpenditure'' data, which refer to 
the proportions of income spent on food for 38 households 
in a large US city (according to the package information). The household expenditures for food are given by
\begin{eqnarray*}
data = FoodExpenditure_{food} / \#(FoodExpenditure_{food}),
\end{eqnarray*}
where $FoodExpenditure_{food}$ is the random variable 
corresponding to the household expenditures for food, and $\#(\cdot)$ indicates the number of observations on this variable. The observations for the first data set are given bellow:\\
  0.4210000, 0.4382105, 0.5721316, 0.1955526, 0.2758158, 0.3565263,
  0.6120000, 0.4730526, 0.3726579, 0.2322368, 0.3732632, 0.5158947,
  0.3612632, 0.5563421, 0.4591053, 0.2533947, 0.3685526, 0.2410526,
  0.4955526, 0.2010789, 0.3653158, 0.2544737, 0.5685263, 0.2859474,
  0.7626316, 0.2863684, 0.4884474, 0.3060263, 0.4754474, 0.3826053,
  0.5050526, 0.6820526, 0.7587632, 0.4176053, 0.3923684, 0.2513158,
  0.6070000, 0.3881842.

Some descriptive statistics are reported in Table \ref{tabds}. The minimum value refers to a family of 3 people and income of 39,151, which does not represent the lowest family 
income for the current data, as expected, occupying only the 
fifth position among those with the lowest income. The maximum value corresponds to a family of 6 people with an income of 69,929, the second-largest number among the number of people per family in the group in question. Furthermore, we can note that the current data  present positive asymmetry and negative kurtosis.

In addition, the standard deviation is relatively low. Figure \ref{ttt} displays the total time on test (TTT) plot for the first data set, which shows that the failure function is decreasing. So, the MOGa-W distribution is appropriate to fit 
these data, since its  hazard function presents this shape (see,  Figure \ref{fig:hazard}).

@@

A data set collected in a pilot study about hypertension in the Dominican Republic in 1997 refers to the second application. The observations are the systolic blood pressure of persons who came to medical clinics in several villages for a variety of complaints. The observations for the data set in question are:

@@

Table \ref{tabds2} provides the descriptive statistics for the second data set. Consi\-dering that the systolic blood pressure represents the highest number presented in the pressure measuring equipment, the maximum (236) found in this 
table should represent an individual with serious heart problems. This is due to the fact that the normal systolic pressure is 120.

The minimum value (80) should be for an individual who probably suffers from low blood pressure. Also note that the data set has positive skewness. This indicates that few people have high pressure values and, in this case, the mode is 120, which represents a good value for systolic pressure.

Figure \ref{ttt2} provides the TTT plot for the second clinic data, which shows that the hazard function is decreasing, thus supporting the MOGa-W model.

@@

\bibitem{Tahir} Tahir, M. H., Nadarajah, S. (2015).  Parameter induction in continuous univariate distributions: Well-established G families. \textit{Anais da Academia Brasileira de Ciências}, {\bf 87}, 539--568.

\bibitem{Eugene} Eugene, N., Lee, C.,  Famoye, F. (2002). Beta-normal distribution and its applications. \textit{Communications in Statistics-Theory and methods}, {\bf 31}, 4, 497--512.

\bibitem{Zografos} Zografos, K., Balakrishnan, N. (2009). On families of beta-and generalized gamma-generated distributions and associated inference. \textit{Statistical methodology}, {\bf 6}, 4, 344--362.
